The Method of Moments

### 2010-12-03 pieces/method-of-moments/method-of-moments.tex
Renamed a bunch of files. Tweaked method of moments.

\begin{document}
\title {Deriving $\lambda$ with the Method of Moments}
\author {Joyce Tipping}
\date{}
\maketitle

\section{Method of Moments}

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
approximations for $\mu$, $\sigma$, and $\lambda$ by comparing the first,
second, and third moments about the mean of $B$ and $Y$.

@@

We can also easily find

@@

The above equation \eqref{eq:solving-for-lambda} is a rational expression in
$\lambda^2$ that can be solved with either a considerable amount of manual
labor or, more efficiently, with a computer algebra system. Once we have
$\lambda^2$, then $\lambda$ is simply either the positive or negative square
root, as determined by the sign of $(1-2p)$: When $p < 0.5$, the binomial skews
left, so $\lambda$ should be negative; when $p > 0.5$, the binomial skews
right, so $\lambda$ should be positive. Thus:

@@

Similarly, with both $\lambda$ and $\sigma$, \eqref{eq:first-moment-set} yields
$\mu$:

@@

\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
approximation. This seems like it ought to be a simple fact, but I can't figure
out how he's getting it from these equations. He refers to his equation (c),
which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
into \eqref{eq:mu-solved}. As far as I can tell, equation
\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}

@@

\begin{equation}
  \min_{v} \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
\end{equation}

>>>>

\begin{document}
\title {The Method of Moments}
\author {Joyce Tipping}
\date{}
\maketitle

\section{The Method of Moments}

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
approximations for $\mu$, $\sigma$, and $\lambda$ by comparing their first,
second, and third moments about the mean.

@@

Having these, we can easily find

@@

The above equation \eqref{eq:solving-for-lambda} is a rational expression in
$\lambda^2$ that can be solved with either a considerable amount of manual
labor or, more efficiently, with a computer algebra system. Once we have
$\lambda^2$, then $\lambda$ is simply either the positive or negative square
root, as determined by the sign of $(1-2p)$: When $p \rightarrow 0$, the
binomial skews left and converges on the positive half normal, so $\lambda$
should be positive; when $p \rightarrow 1$, the binomial skews right and
converges on the negative half normal, so $\lambda$ should be negative; and
when $p = 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the
need for a sign. Thus:

@@

Similarly, with both $\lambda$ and $\sigma$, a simple rearrangement of
\eqref{eq:first-moment-set} yields $\mu$:

@@

\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
approximation. This seems like it ought to be a simple fact, but I can't figure
out how he's getting it from these equations. He refers to his equation (c),
which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
into \eqref{eq:mu-solved}. And as far as I can tell, equation
\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}

@@

\begin{equation}
  \min_{v} \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
\end{equation}
